---
title: "Registering A Consumer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RegisteringAConsumer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE, 
  warning = FALSE, 
  message = FALSE
)
```

## Overview

-   For all of the fields that can be passed to the `register_consumer()` function, see the table below.

-   For more information about the Bloom Credit API Consumers endpoint, see the documentation [here](https://developers.bloomcredit.io/reference/createconsumerv2 "Bloom Credit - Create A Consumer API Documentation").

```{r setup}
library(readr)
library(dplyr)
library(gt)

consumer <- readr::read_csv("consumer.csv", show_col_types = FALSE)
```

## Creating `consumer_info` List

`{bloomR}` expects a list of consumer information to be passed into the `register_consumer()` function.

Example list with all required fields:

```{r, eval = FALSE, echo = TRUE}

consumer_info <- list(
  ssn = "123456789",
  city = "Scranton",
  line1 = "1725 Slough Avenue",
  state_code = "PA",
  zipcode = "18503",
  date_of_birth = "1964-03-15",
  first_name = "Michael",
  last_name = "Scott",
  address_primary = TRUE
)

consumer_id <- register_consumer(
  audience = "dev",
  consumer_info = consumer_info,
  auth_token = "your_auth_token"
)

```

## Required Fields

See the table below for all required fields.

```{r}
consumer %>% 
  filter(Required) %>% 
  gt::gt()
```

## All Fields

See the table below for all fields.

```{r}
consumer %>% 
  mutate(Required = ifelse(is.na(Required), FALSE, TRUE)) %>% 
  gt::gt()
```
