---
title: "Using {bloomR}"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{UsingbloomR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(bloomR)
```

## Credential Management

When managing your `client_id` and `client_secret`, refer to the Bloom Credit API guidance:

> All requests to the Bloom API require a valid Oauth2 Access Token to be present in the `Authorization`header. You can think of this Access Token like an API key, it is what grants you access to the API.
>
> Bloom will provide you with two credentials:
>
> (1) **Client ID**\
> and\
> (2) **Client Secret**
>
> These two credentials are what you will use to request an Access Token. You will do so using the Oauth2 `client_credentials` grant flow which will be explained below.
>
> While your provided **Client ID** is considered a "public" credential, your **Client Secret** must only be known by your backend application(s). It must never be included in any front-end applications, stored in plaintext, or transmitted across unsecured (non-SSL) connections. Treat it as you would a password.

### [Option 1]: Storing Secrets In Your R Environment

`{bloomR}` provides two functions that allow you to store your `client_id` and `client_secret` in your R options.

**⚠️ Use these functions carefully and make sure that you are stroring your credentials appropriately.**

```{r, echo = TRUE, eval = FALSE}
# set your client id
bloomR::set_client_id(
  client_id = "your_client_id"
)

bloomR::set_client_secret(
  client_secret = "your_client_secret"
)
```

As long as these credentials persist, this will allow you to fetch your `auth_token` without needing to provide credentials every time you need to refresh your token:

```{r, eval = FALSE}
# fetch Oauth2 token
auth_token <- fetch_auth_token(
  audience = "dev"
)
```

### [Option 2]: Providing Secrets When Fetching Token

You can also choose to use a password manager or other secure method to store your credentials, and only pass them to `{bloomR}` when fetching your `auth_token`.

When running `fetch_auth_token()`, you will be prompted to paste your credentials.

Or, you can store credentials temporarily in your environment and pass them to `fetch_auth_token()`:

```{r, eval = FALSE}
# set credentials
client_id <- "your_client_id"
client_secret <- "your_client_secret"

# fetch Oauth2 token
auth_token <- fetch_auth_token(
  audience = "dev",
  client_id = client_id,
  client_secret = client_secret
)
```

## Registering A Consumer

To register a consumer, you will need to construct a list with all required fields, as well as your `auth_token`.

See the **Registering A Consumer** vignette for more details about constructing the `consumer_info` list.

#### 1). Create `consumer_info` List

```{r, eval = FALSE}

consumer_info <- list(
  ssn = "123456789",
  city = "Scranton",
  line1 = "1725 Slough Avenue",
  state_code = "PA",
  zipcode = "18503",
  date_of_birth = "1964-03-15",
  first_name = "Michael",
  last_name = "Scott",
  address_primary = TRUE
)
```

#### 2). Register Consumer

```{r, eval = FALSE}
consumer_id <- register_consumer(
  audience = "dev", 
  consumer_info = consumer_info, 
  auth_token = auth_token
  )
```

## Place An Order

After you register a consumer, you can then place an order for a credit report for any SKUs that are enabled for your account.

-   `audience`: values "dev" or "prod" are accepted, corresponding to the "sandbox" and "production" environments. For more detail, see [the API documentation](https://developers.bloomcredit.io/docs/environments-1#per-environment-parameters).

-   `consumer_id`: value returned from `bloomR::register_consumer()`. Optionally, you can save or fetch IDs and pass them in directly.

-   `portfolio_id`: your portfolio ID.

-   `sku`: any SKU enabled for your account.

-   `auth_token`: your Oauth2 token.

```{r, eval = FALSE}
credit_order <- order_credit_data(
  audience = "dev", 
  consumer_id = consumer_id, 
  portfolio_id = "your_portfolio_id", 
  sku = "equifax-gold-soft-fico-internet",
  auth_token = auth_token
  )
```

## Retrieving Credit Data

After you have placed an order for credit data for a consumer, you can parse the data to a list of `data.frames` for review.

-   `audience`: values "dev" or "prod" are accepted, corresponding to the "sandbox" and "production" environments. For more detail, see [the API documentation](https://developers.bloomcredit.io/docs/environments-1#per-environment-parameters).
-   `order_id`: value returned from `credit_order$data$id`.
-   `auth_token`: your Oauth2 token.

```{r, eval = FALSE}
credit_data <- get_credit_data(
  audience = "dev",
  order_id = credit_order$data$id,
  auth_token = auth_token
)
```
